\chap{Acknowledgements}

%%%% there is no specific formatting requirement for this section 
%% default is double-spaced (you can style it as you want)
% \lipsum[1-2]

There are so many people who contributed to the work described in this thesis. But certainly, none of this would have been possible without a steady hand on the tiller and a steely vision of the research landscape. 

Andrei, thank you so much for your relentless support and passion for good science. You have been an inspiration many times during my PhD, and it must be made clear how appreciated you are in your role as a researcher, advisor, and guiding force. 

Savvas, our dear postdoc, thank you sincerely for the effort you put into this analysis and our group. You kept things moving, even when unexpected challenges presented themselves, and you reliably provided a voice of reason when the going got tough. You were a collaborator and friend the whole way, as we figured things out together. 

Mohit, my off-shell heir apparent, I will always appreciate your skills, camaraderie, and wit. Same goes for Nick, Zhiyuan, and Jeff, my CMS comrades in the trenches. Thank you all for making this group what it is now, and for being fantastic colleagues and companions these past few years. 

Toni, how great is it that we got to spend so much time with you. Thank you for the chats, advice, and motivation over the years. You've always been a great collaborator but now you've added incredible liveliness and enthusiasm to our group and it's a blessing to end my PhD journey on such a note. 

I might as well mention others in the Hopkins HEP family: Morris, Petar, Danielle, thank you for the conversations and insights, even with our limited cross-section it was very enjoyable. 

Michalis, Lucas, Valdis, Ruoxi, Sanjana, it was a pleasure to overlap as much as we did. I'm glad we got to spend some time together and occasionally even get to work together. 

Toby, Bob, thank you as well for the conversations we've had. It was very nice to have your perspectives, unconditional support, and advice. 

And of course, I need to thank my past academic advisors, who have inspired and molded my academic journey. Stephen, Meenakshi, Jim, you have taught and helped me so much through my research career. Thank you. 

Finally, I wouldn't be here without my family. Mom, thank you for always putting in the work and enriching our lives. You always prioritized our education and interests above all, and I owe everything to you. Dad, I appreciate your constant exploration and passion. And Louis and Lawrence, I'll always admire your tenacity and brilliance---you both inspire me everyday. 
